---
output:
  md_document:
    variant: markdown_github
---
[![Project Status: Inactive ? The project has reached a stable, usable state but is no longer being actively developed; support/maintenance will be provided as time allows.](http://www.repostatus.org/badges/latest/inactive.svg)](http://www.repostatus.org/#inactive)
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![Build Status](https://travis-ci.org/privefl/primefactr.svg?branch=master)](https://travis-ci.org/privefl/primefactr)
[![codecov](https://codecov.io/gh/privefl/primefactr/branch/master/graph/badge.svg)](https://codecov.io/gh/privefl/primefactr)
 
---
 
```{r, echo = FALSE}
description <- readLines("DESCRIPTION")
rvers <- stringr::str_match(grep("R \\(", description, value = TRUE), "[0-9]{1,4}\\.[0-9]{1,4}\\.[0-9]{1,4}")[1,1]
```
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r rvers`-6666ff.svg)](https://cran.r-project.org/)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/primefactr)](https://cran.r-project.org/package=primefactr)
```{r, echo = FALSE}
description <- readLines("DESCRIPTION")
version <- gsub(" ", "", gsub("Version:", "", grep("Version:", description, value = TRUE)))
```
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)
 
---
 
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
 
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# primefactr
R package that uses Prime Factorization for computations.

This small R package was initially developed to compute [hypergeometric probabilities](https://en.wikipedia.org/wiki/Hypergeometric_distribution) which are used in Fisher's exact test, for instance.

## Installation and Attachment

```{r, eval=FALSE}
## Installation
install.packages("primefactr")

## Attachment
library("primefactr")
```

## Features

### Main feature
- To compute $P(X = k) = \dfrac{\binom{K}{k}~\binom{N-K}{n-k}}{\binom{N}{n}} = 
\dfrac{K!~(N-K)!~n!~(N-n)!}{k!~(K-k)!~(n-k)!~(N-K-n+k)!~N!}$
